---
title: "P8105_hw5_hy2669"
author: "haoyang,yi"
date: "2020/11/10"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
knitr::opts_chunk$set(
  fig.width = 8,
  fig.asp = 0.7,
  fig.height = 8,
  out.width = '90%'
)
theme_set(theme_minimal())
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```
## Problem 1
### read and tidy the dataset
```{r message= F}
homicide_df = read_csv("data/homicide_data/homicide-data.csv") %>%
  mutate(city_state = str_c(city,state,sep = '_'),
         resolved = case_when(
           disposition == 'Closed without arrest' ~ "unsolved",
           disposition == 'Open/No arrest' ~ "unsolved",
           disposition == 'Closed by arrest' ~ "solved",
         )) %>%
  select(city_state,resolved) %>%
  filter(city_state != "Tulsa_AL") 
```
### summarize
```{r message= F}
aggregate_df = homicide_df %>%
  group_by(city_state) %>%
  summarize(hom_total = n(),
            hom_unsolved = sum(resolved == "unsolved"))
```
### obtain results of proportion tests
```{r}
results_df = aggregate_df %>%
  mutate(prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
         tidy_tests = map(.x = prop_tests, ~broom::tidy(.x))) %>%
  select(-prop_tests) %>%
  unnest(tidy_tests) %>%
  select(city_state,estimate,conf.low,conf.high)
```
make plot
```{r}
results_df %>%
  mutate(city_state = fct_reorder(city_state,estimate)) %>%
  ggplot(aes(x = city_state, y = estimate))+
  geom_point()+
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))+
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust = 0.1))
  
```

## Problem 2
### read and tidy the data
```{r warning=F, message=F}
file_name = list.files('./data/lda_data') # get the names of 20 csv.files
arm_df = tibble(file_name = file_name) %>% # start with a dataframe containing all file names.
  bind_cols(map_df(str_c('./data/lda_data/',file_name), read_csv)) %>% # read data from 20 csvs, save the results in arm_df.
  separate(file_name, into = c('arm_type', 'id')) # tidy the dataset, separate file_name(con01) into arm_type(con/exp) and id(1-10).
  knitr::kable(arm_df) # show the tidy dataset. Weekly observations are tidy.
```

### make a spaghetti plot
```{r}
arm_df %>%
  pivot_longer(week_1:week_8,
               names_to = 'week',
               names_prefix = 'week_',
               values_to = 'observation') %>% # combine weekly observations in a column for making plot
  mutate(arm_id = str_c(arm_type,id)) %>% # combine arm_type and id again 
  group_by(arm_id) %>%
  ggplot(aes(x = week, y = observation, color = id, group = arm_id))+
  geom_line(alpha = 0.6)+
  geom_point(aes(shape = arm_type), alpha = 0.8, size = 2.5)+ # use aes(shape = ) to create points with distinct shape from two types of arm.
  labs(title = "Observations on each subject over time", x = "Week", y = "Observation")+
  theme(legend.position = "bottom", plot.title = element_text(hjust = .5))
```
  Over the 8 weeks the observations of experiment group has a increasing trend while observations of control groups stayed the same with little fluctuations. After 8 weeks the observations of experiment group are higher than control group in all 10 subjects

## Problem 3
### Create the function 
```{r}
set.seed(1)
norm_fun <- function(mu,n = 30, sigma = 5) # default setup: n = 30, sigma = 5
{
  sim_data = tibble(x = rnorm(n,mean = mu,sd = sigma),)
  sim_data %>%
    mutate(mu_hat = broom::tidy(t.test(sim_data))$estimate,
           p_value = broom::tidy(t.test(sim_data))$p.value) %>%
    select(-x) %>%
    distinct()
}
```
### Simulation for mu = 0,1,2,3,4,5,6
```{r}
sim0_df = rerun(5000,norm_fun(mu = 1)) %>%
  bind_rows() # Generate 5000 normal(mu = 0, sigma = 5, n = 30) simulation and store the results of t.test(H0 : mu = 0)

sim_df <- tibble(mu = c(0:6)) %>% # expand simulation to mu = 0,1,2,3,4,5,6
  mutate(output_list = map(.x = mu, ~rerun(5000, norm_fun(mu = .x))),
         result_df = map(output_list,bind_rows)) %>%
  select(-output_list) %>%
  unnest(result_df) %>%
  mutate(Null_hypothesis = ifelse(p_value >= 0.05, "Fail to reject",'Reject'))  # Decision rule of t-test: If p_value < 0.05, reject H0, otherwise fail to reject H0
  head(sim_df)
```

### Make a plot to show association between effect size and power.
```{r message = F, warning = F }
sim_df %>%
  group_by(mu) %>%
  summarize(power = sum(Null_hypothesis == 'Reject')/n()) %>% # calculate power when mu = 0:6 
  ggplot(aes(x = mu, y = power))+
  geom_point(size = 2)+
  geom_line(alpha = 0.6)+
  geom_smooth(alpha = 0.3,size = 0.5)+
  labs( title = "Association between effect size and power",
        x = "True value of μ",
        y = "Power") +
  theme(plot.title = element_text(hjust = .5))
```
  As effect size increases, power increases, when effect size is high enough (in this case: mu >= 4), power is approximately equal to 1. 

### Make a plot showing the average estimate of μ^ on the y axis and the true μ 
```{r message = F, warning = F}
sim_df %>%
  group_by(mu) %>%
  summarize(average_mu_hat = mean(mu_hat)) %>%
  ggplot(aes(x = mu, y = average_mu_hat))+
  geom_point(size = 2)+
  geom_line(alpha = 0.6)+
  labs( title = "Association between true μ and average estimate of μ^",
        x = "True value of μ",
        y = "Average estimate of μ^") +
  theme(plot.title = element_text(hjust = .5))
```
  Clearly the average estimate of mu_hat is approximately equal to true mu in this 5000 times simulation for mu = 0,1,2,3,4,5,6

### Make a plot showing the average estimate of μ^ on the y axis and the true μ in samples for which the null was rejected

```{r message = F, warning = F}
sim_df %>%
  filter(Null_hypothesis == 'Reject') %>%
  group_by(mu) %>%
  summarize(average_mu_hat = mean(mu_hat)) %>%
  ggplot(aes(x = mu, y = average_mu_hat))+
  geom_point(size = 2)+
  geom_line(alpha = 0.6)+
  labs( title = "Association between true μ and average estimate of μ^ when H0 is rejected",
        x = "True value of μ",
        y = "Average estimate of μ^") +
  theme(plot.title = element_text(hjust = .5))
```
  Across test for which the null hypothesis is rejected, when true mu = 0,1,2,3, which means true mu is close to the null hypothesis(mu = 0), the average estimate of mu_hat is not equal to true value of mu, since . But when true mu is so large that the null hypothesis is always rejected, the average estimate of mu_hat is approximately equal to true value of mu. 
